A simulation framework for exploring spatio-temporal dynamics in mixed fisheries

### 2018-01-30 write_up/mixfishsim_ecolmod.tex
Updates to manuscript

\begin{abstract}
[A concise and factual abstract is required. The abstract should state briefly
the purpose of the research, the principal results and major conclusions. An
abstract is often pnresented separately from the article, so it must be able to
stand alone. For this reason, References should be avoided, but if essential,
then cite the author(s) and year(s). Also, non-standard or uncommon
abbreviations should be avoided, but if essential they must be defined at their
first mention in the abstract itself.  
Graphical abstract: Although a graphical abstract is optional, its use is
encouraged as it draws more attention to the online article. The graphical
abstract should summarize the contents of the article in a concise, pictorial
form designed to capture the attention of a wide readership. Graphical
abstracts should be submitted as a separate file in the online submission
system. Image size: Please provide an image with a minimum of 531 X 1328 pixels
(h X w) or proportionally more. The image should be readable at a size of 5 x
13 cm using a regular screen resolution of 96 dpi.  Preferred file types: TIFF,
EPS, PDF or MS Office files.]
\end{abstract}

@@

\begin{equation*}
	\begin{split}
 (x2, y2) =  & x1 + StepL \cdot \cos (\frac{\pi \cdot Br}{180}), \\
             & y1 + StepL \cdot \sin (\frac{\pi \cdot Br}{180}) \\	
 where \hspace{0.5cm}     & Br \sim U[(0,360)]
	\end{split}
\end{equation*}

@@

[Guidance: A Theory section should extend, not repeat, the background to the
article already dealt with in the Introduction and lay the foundation for
further work.  In contrast, a Calculation section represents a practical
development from a theoretical basis.]

HERE DESCRIBE THE PARAMETERISATION, AND ANY COMPARISON AGAINST 'REAL' DATA

@@

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{../tests/plots/habitat}
		\caption{habitat}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{../tests/plots/annual_summary}
		\caption{Annual Summmary}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{../tests/plots/fDynamics}
		\caption{f dynamics}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{../tests/plots/vessel_move}
		\caption{vessel movement}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{../tests/plots/vessel_multi_move}
		\caption{vessel movement multi}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{../tests/plots/vessel_move_value}
		\caption{vessel movement value}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{../tests/plots/fleet_moves}
		\caption{fleet movement}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{../tests/plots/catch_comp}
		\caption{spatial catch composition}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{../tests/plots/catch_comp_clusters}
		\caption{spatial catch composition with clustering}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{../tests/plots/survey_index}
		\caption{survey index}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{../tests/plots/spatial_survey}
		\caption{survey spatial abundance}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{../tests/plots/step_function}
		\caption{Realised step function}
\end{figure}

>>>>

\begin{abstract}
[Guidance: A concise and factual abstract is required. The abstract should
state briefly the purpose of the research, the principal results and major
conclusions. An abstract is often pnresented separately from the article, so it
must be able to stand alone. For this reason, References should be avoided, but
if essential, then cite the author(s) and year(s). Also, non-standard or
uncommon abbreviations should be avoided, but if essential they must be defined
at their first mention in the abstract itself.  Graphical abstract: Although a
graphical abstract is optional, its use is encouraged as it draws more
attention to the online article. The graphical abstract should summarize the
contents of the article in a concise, pictorial form designed to capture the
attention of a wide readership. Graphical abstracts should be submitted as a
separate file in the online submission system. Image size: Please provide an
image with a minimum of 531 X 1328 pixels (h X w) or proportionally more. The
image should be readable at a size of 5 x 13 cm using a regular screen
resolution of 96 dpi.  Preferred file types: TIFF, EPS, PDF or MS Office
files.]
\end{abstract}

@@

\begin{equation*}
	\begin{split}
 (x2, y2) =  & x1 + StepL \cdot \cos (\frac{\pi \cdot Br}{180}), \\
             & y1 + StepL \cdot \sin (\frac{\pi \cdot Br}{180}) \\	
 with  \hspace{0.5cm}     & Br_{t-1} < 180, Br_{t} = 180 + \sim vm[(0,360), k] \\
 			  & Br_{t-1} > 180, Br_{t} = 180 - \sim vm[(0,360), k] \\
	\end{split}
\end{equation*}

with $k$ the concentration parameter from the von mises distribution which we
correlate with the revenue so that $k = (revenue + 1 / maxRevenue) * max_{k}$

where $max_{k}$ is the maximum concentration value, $k$, and maxRevenue is
parameterised as for $\beta_{3}$ in the step length function. \\

@@

[Guidance: A Theory section should extend, not repeat, the background to the
article already dealt with in the Introduction and lay the foundation for
further work.  In contrast, a Calculation section represents a practical
development from a theoretical basis.] \\

\subsection{Simulation settings}

We set up with simulation to run for 20 years based on a 100 X 100 square grid,
with five fleets of 20 vessels each and four fish populations. Fishing takes
place four times a day per vessel and five days a week, while population
movement is every two weeks. \\

\subsection{Population parameterisation}

We parameterised the simulation model for four populations with differing
habitat preference (Figure \ref{fig:1}) and defined two spawning areas for each
of the populations (Table \ref{tab:1}). \\

\begin{table}[!ht]
\caption{Population dynamics and movement parameter setting}
	\begin{tabular}{ p{4cm } p{2cm} p{2cm} p{2cm} p{2cm}}
	Parameter & Pop 1 & Pop 2 & Pop 3 & Pop 4 \\
	\hline
	Habitat quality & & & \\
	\hline
	Matérn $\nu$ & 1/0.15 & 1/0.05 & 1/0.55 & 1/0.05  \\
	Matérn $\kappa$ & 1 & 2 & 1 & 1  \\
	Anisotropy & 1.5,3,-3,4 & 1,2,-1,2 & 2.5,1,-1,2 & 0.1,2,-1,0.2 \\
	Spawning areas (bound box) & 40,50,40,50; 80,90,60,70 &
	50,60,30,40; 80,90,90,90 & 30,34,10,20; 60,70,20,30 & 50,55,80,85; 30,40,30,40 \\
	Spawning multiplier & 10 & 10 & 10 & 10 \\
	Movement $\lambda$ & 0.3 & 0.3 & 0.3 & 0.3 \\
	\hline
	Population dynamics & & & & \\
	\hline
	Starting Biomass & 1e5 & 2e5 & 1e5 & 1e4 \\
	Beverton-Holt Recruit 'a' & 60 & 100 & 80 & 2 \\
	Beverton-Holt Recruit 'b' & 250 & 250 & 200 & 50 \\
	Beverton-Holt Recruit $\sigma$ & 0.2 & 0.1 & 0.2 & 0.1 \\
	Recruit week & 13-16 & 12-16 & 14-16 & 16-20 \\
	Population dynamics and movement parameter settingSpawn week & 16-18 & 16-19 & 16-18 & 18-20 \\
	M (annual) & 0.2 & 0.2 & 0.2 & 0.1 \\
	\hline
\end{tabular}
\label{tab:1}
\end{table}

\subsection{Fleet parameterisation}

\begin{table}[!ht]
\caption{Fleet dynamics parameter setting}
\begin{tabular}{ p{4cm } p{1cm} p{1cm} p{1cm} p{1cm} p{1cm}}
	\hline
	Parameter & Fleet 1 & Fleet 2 & Fleet 3 & Fleet 4 & Fleet 5 \\
	\hline
	Targeting preferences &&&& \\
	\hline
	Price Pop1 & 100 & 100 & 100 & 100 & 100 \\
	Price Pop2 & 200 & 200 & 200 & 200 & 200 \\
	Price Pop3 & 600 & 600 & 600 & 600 & 600 \\
	Price Pop4 & 1600 & 1600 & 1600 & 1600 & 1600 \\
	$Q$ Pop1 & 0.01 & 0.02 & 0.02 & 0.02 & 0.02 \\
	$Q$ Pop2 & 0.02 & 0.01 & 0.01 & 0.01 & 0.01\\
	$Q$ Pop3 & 0.01 & 0.02 & 0.02 & 0.02 & 0.02 \\
	$Q$ Pop4 & 0.02 & 0.01 & 0.01 & 0.01 & 0.01 \\
	\hline
	Exploitation dynamics &&&& \\
	\hline
	step function $\beta_1$ & 1 & 2 & 1 & 2 & 3 \\
	step function $\beta_2$ & 10 & 10 & 8 & 12 & 7 \\
	step function $\beta_3$ & MaxRev & MaxRev & MaxRev & MaxRev & MaxRev \\
	step function $rate$ & 10 & 20 & 15 & 25 & 10 \\
	Past Knowledge & T & T & T & T & T \\
	Past Year \& Month & T & T & T & T & T \\
	Past Trip & T & T & T & T & T \\
	Threshold & 0.75 & 0.75 & 0.75 & 0.75 & 0.75 \\
	\hline
\end{tabular}
\label{tab:2}
\end{table}

@@

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{../tests/plots/habitat}
	\caption{habitat preference}
	\label{fig:1}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{../tests/plots/annual_summary}
	\caption{Annual Summmary}
	\label{fig:2}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{../tests/plots/fDynamics}
	\caption{f dynamics}
	\label{fig:3}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{../tests/plots/vessel_move}
	\caption{vessel movement}
	\label{fig:4}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{../tests/plots/vessel_multi_move}
	\caption{vessel movement multi}
	\label{fig:5}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{../tests/plots/vessel_move_value}
	\caption{vessel movement value}
	\label{fig:6}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{../tests/plots/fleet_moves}
	\caption{fleet movement}
	\label{fig:7}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{../tests/plots/catch_comp}
	\caption{spatial catch composition}
	\label{fig:8}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{../tests/plots/catch_comp_clusters}
	\caption{spatial catch composition with clustering}
	\label{fig:9}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{../tests/plots/survey_index}
	\caption{survey index}
	\label{fig:10}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{../tests/plots/spatial_survey}
	\caption{survey spatial abundance}
	\label{fig:11}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{../tests/plots/step_function}
	\caption{Realised step function}
	\label{fig:12}
\end{figure}
